Analyse gender in music psychology from journal publication data

### 2025-09-27 manuscript/_figure1.qmd
Presubmission version, ready for colleagues to read.

```{r}
#| label: fig1
#| fig-width: 9
#| fig-height: 4.75
#| echo: false
#| warning: false
#| message: false
#| fig.cap: > 
#|   Authorship types across time.

>>>>

```{r}
#| label: fig1
#| fig-width: 9
#| fig-height: 4.75
#| echo: false
#| warning: false
#| message: false
#| fig.cap: > 
#|   Authorship types across time

### 2025-09-27 manuscript/_figure2.qmd
Presubmission version, ready for colleagues to read.

```{r}
#| label: fig2
#| fig-width: 13
#| fig-height: 4
#| echo: false
#| warning: false
#| message: false
#| fig.cap: > 
#|   A) Number of authors and B) female odds ratio for authorship types across the number of authors.

>>>>

```{r}
#| label: fig2
#| fig-width: 13
#| fig-height: 4
#| echo: false
#| warning: false
#| message: false
#| fig.cap: > 
#|   A) Number of authors and B) female odds ratio for authorship types across the number of authors

### 2025-09-27 manuscript/manuscript-apaquarto.qmd
Presubmission version, ready for colleagues to read.

title             : "Gender Distribution of Authors in Music Psychology"

@@

  apaquarto-docx: default

@@

#_  apaquarto-typst: 
#_    keep-typ: true
#_    list-of-figures: false
#_    list-of-tables: false

@@

Academia suffers various equity issues, impacting productivity, innovation, and job satisfaction in the workplace, which-in turn-hugely impact academic progress. Although there are several aspects, the focus of this paper is gender inequity. Women are more at a disadvantage than men, with evidence suggesting that women are less present in positions of power. For instance, in the UK in 2016-17, 24.6% of professors are women [@bhopal2021competing] when compared to the 44% of all grades in the UK academia [@harris2025gender]. A similar situation holds for Italy (24% female professors) [@Filandri03082021], and to some extent for the United States (14%) [@spoon2023]. A pay gap between men and women in academia is also significant, (e.g., female-male wage ratio is 0.85 in 2020 in the United Kingdom) [@quadlin2023higher]. In a “publish or perish” culture of science and academia [@kiai2019protect], one crucial aspect to focus on is authorship. The number and quality (e.g., journal reputation) of authorships an individual determines crucial career development such as grant funding and future (permanent) positions.

@@

Authorship is a crucial marker of scholarly success in academia, which strongly influences academic career progression, recognition, funding, and advancement opportunities. However, there are several inequities within academic authorship, with women often being underrepresented. As male-female authorship representations differ across different academic disciplines, it is worthwhile diagnosing the situation in the field of music psychology. The goal of the current paper was to provide a snapshot of authorship prevalence and roles across gender in core music psychology journals, specifically _Musicae Scientiae_, _Psychology of Music_, _Music Perception_, _Journal of New Music Research_, and _Music & Science_. Overall, we found that the distribution of authors by gender remains unequal, with women representing 40.2% of authors. This proportion is higher than in musicology [34.8% in @eerola2026inprep] and higher than in psychology more broadly, where women account for a third of authors [33.2% in @huang2020; 36.2%in @gonzalez2020women]. This representation is also much higher than in other STEM subjects of math, physics and computer science [15% in @huang2020] and topics such as astronomy and bioscience [17.8% in @son2022scientific]. While our current findings suggests that the field of music psychology is doing better in fostering gender equity than certain other fields, women are still overall underrepresented. In exploring the nuances behind this, we further analysed differences between authorship role, number of citations, geography, and article keywords.

In terms of authorship roles, notable differences emerge. Women are more likely than men to appear as first authors, a trend that has become characteristic of the field only in the past 15 years. This supports previous research showing that there is a positive trend with female representation increasing [@gonzalez2020women; @ioannidis2023gender; @jemielniak2025gender; @sanchez2024analysis]. In contrast, women remain underrepresented in the last authorship position, and this trend has not changed substantially over the last 15 years. This underrepresentation in woman as last authors corresponds to the situation in other academic fields such as medicine [@bruck2023bibliometric; @shah2021gender], psychology [@gonzalez2020women], and biology [@rock2021quantifying]. Although last authorship in the social sciences is not necessarily universally defined, it is nonetheless increasingly associated with seniority, supervisory responsibility, or principal investigator status [@drivas2024evolution]. Therefore, this underrepresentation suggests that women are less likely to occupy leadership roles such as lab heads or holders of substantial research resources. This pattern is consistent with broader evidence showing that women remain underrepresented in senior academic positions, including professorial appointments [@bakker2016tenure], invitations to contribute to journals, and authorship in high-prestige outlets [@holman2018gender]. Related analyses from science and medicine further show that women are more often associated with conducting experiments, whereas men are disproportionately represented in authorship roles linked to leadership and oversight [@macaluso2016science]. This patterns is also consistent with the idea of a "leaky pipeline", where women are more likely to drop away from academic careers with increasing seniority, especially between doctoral and (consolidated) researcher positions [@gonzalez2020women] and generally have shorter academic careers [@sanchez2024analysis]. On a broader level, this might highlight the need for more mentorship programs for (junior) women to senior positions. Indeed, mentorship programs have been shown support remaining in academia [@gardiner2007show]. We note that within the broader music psychology community, there are some mentorship programs in place, for example, Women in Music Information Retrieval WIMIR (https://wimir.wordpress.com/) and the Society for Music Perception and Cognition has resources for trainees and a Mentorship committe (https://www.musicperception.org/committees) and often holds mentor-mentee meetings at conferences. Although these measures have been in places for some years, it might still take some time for the effect to translate and additional mentorship programs could be welcome.

@@

Turning to potential drivers of these gender differences, geographical and cultural factors appear to play a major role. Our summaries of gender patterns across continents and countries indicate clear cross-national variation, supporting the idea that certain inequity may stem from national cultural factors [@bruck2023bibliometric]. Large Commonwealth nations, namely Australia, Canada, and the United Kingdom, seem to provide a cultural climate more supportive of women in research, as reflected in the relatively high odds ratios of women appearing as authors (in any authorship position) in music psychology. This pattern, however, is not universal across all countries examined [@chan2020]. Prior work shows that women’s research success can be positively correlated with national indicators of gender equity [@chan2020] or are related to countries with intermediate Human Development Index [@sanchez2024analysis; @sugimoto2015relationship]. This discrepancy between author representation could likely to be related to a career length, which strongly correlates with overall productivity. Women exhibit higher dropout rates than men, particularly during the 5–10 years following their first publication [@huang2020], but policies geared towards equity and support for career breaks and caring responsibilities may well contribute towards the observed country-specific differences. Nevertheless, prior analyses demonstrate that even when women constitute a smaller share of researchers within a discipline or country, their contributions are often more impactful than those of their male colleagues [@chan2020]. When examining countries where women have significantly lower odds of authorship compared to men (Japan, Belgium, Austria, Sweden, and Turkey), it is not straightforward to conclude that the lower proportion of female author is related gender equality rankings. The notable exception is Turkey, which is positioned lower according to the Gender Inequality Index [@UNDPHDR2024].

The keyword analysis of the articles indicated thematic differences in the topics studied by women and men. Research areas related to children, well-being, health, and mental health were more frequently associated with women. This pattern is consistent with observations in psychology more broadly, where women are more strongly represented in sub-disciplines that focus on (health)care and nurturing [@bruck2023bibliometric; @gonzalez2020women]. The higher likelihood of women studying topics related to singing may be connected to prevailing gender stereotypes, or to the early negative perceptions of singing among boys [@Warzecha2013] and men [@palkki2015gender]. In contrast, topics related to cognition and computation were more often associated with men, which reflects a wider trend in psychology [@gonzalez2020women]. In a similar trend in computational linguistics, woman are more likely to publish on speech, social and conversational topics than males, who are more likely to publish in formal mathematical, syntax, and semantic approaches [@vogel2012he]. The difference that female prefer 'caring' topics over male authors fits with the general idea that female researchers value research on societal progress, while males prefer research aimed at scientific progress [@zhang2021gender]. This fits with another potential explanation for the disparity between authorship, namely that women might also lean toward and execute more university/campus/departmental services than men [@guarino2017faculty]. Over time, performing such services to universities are time away from other work on acquiring funding and leading research, which would aggregate over time to time away from publishing research. It is nonetheless important for such services are completed; in some cases it could be there is more encouragement for males to take on these kinds of roles, but also it could be that success in academia could also be more societal defined as not only publications [@kiai2019protect], but as a whole should celebrate achievements that support internal, local and community services in a broader sense.

There are certain limitations of the current research. The gender of the authors are not part of the database - gender was inferred based on author name using _genderize API_ [@wais2006]. Nonetheless, we maintain that the conclusions may still hold. First, both authors checked whether any of the gender attribution of major names needed fixing (see accompanying code). Second, there error (confidence) of the gender attribution was relatively small (only `89` had low (< 0.55) attribution probability, while 89.3% had high (> 0.90) attribution probability), so it is unlikely that the remaining names would significantly change the main conclusions. Another limitation is treating gender as a binary category. While we recognise that gender is a complex and multidimensional social construct, we used a binary male-female classification consistent with prior meta-science research on gender and authorship [@son2022scientific; @shah2021gender; @rock2021quantifying; @ni2021gendered; @gonzalez2020women; @wais2006] and because generally the number of non-binary authors is currently relatively low [0.8% in @son2022scientific]. Nonetheless, future research should also move towards using more inclusive, non-binary information. However, the main limitation is that such research indicates the symptoms of certain issues in academia, but not necessarily the causes. While we speculate on certain reasons for the current state of affairs, other kinds of research such as qualitative and longitudinal research would further elucidate the key problems, and where areas for improvements could be made to promite better equity in academia.

<!-- I did not know what these references signaled, so temporarily disabled them: -->

<!-- @ashmos2011gendering : women publish more qualitative studies than men -->

<!-- @sebo2020gender : women were more likely to publish qualitative studies and to publish in primary healthcare journals -->

<!-- @thelwall2019gender : women are likely to use exploratory and qualitative methods rather than quantitative methods. -->

@@

The analysis of gender distributions in the five most prominent music psychology journals over the last 25 years presented a rich and evolving history of gender distribution in various authorship roles. While overall women hold smaller number of authorship overall (`{r} round(nrow(dplyr::filter(df,Gender=='female'))/nrow(df),3)*100`%), they are significantly more likely to hold first author positions in coauthored publications but significantly less likely likely to hold last author positions than men. For solo publications and being a coauthor, there are no significant gender differences.

@@

>>>>

title             : "The Gendered Nature of Authorship in Music Psychology"

@@

#_  apaquarto-docx: default

@@

  apaquarto-typst: 
    keep-typ: true
    list-of-figures: false
    list-of-tables: false

@@

Academia suffers various equity issues, impacting productivity, innovation, and job satisfaction in the workplace, which-in turn-hugely impact academic progress. Although there are several aspects, the focus of this paper is gender inequity. Women are more at a disadvantage than men, with evidence suggesting that women are less present in positions of power. For instance, in the UK in 2016-17, 24.6% of professors are women [@bhopal2021competing] when compared to the 44% of all grades in the UK academia [@harris2025gender]. A similar situation holds for Italy [24% female professors, @Filandri03082021], and to some extent for the United States [14%, @spoon2023]. A pay gap between men and women in academia is also significant, (e.g., female-male wage ratio is 0.85 in 2020 in the United Kingdom) [@quadlin2023higher]. In a “publish or perish” culture of science and academia [@kiai2019protect], one crucial aspect to focus on is authorship. The number and quality (e.g., journal reputation) of authorships an individual determines crucial career development such as grant funding and future (permanent) positions.

@@

A crucial marker of scholarly success in academia is authorship, which strongly influences career progression, recognition, funding, and advancement opportunities. However, there are several inequities within academic authorship, where women are often underrepresented. As male-female authorship representations differ across different academic disciplines, the goal of the current paper was to provide a snapshot of authorship prevalence and roles across gender in the field of music psychology. An analysis of papers from five core music psychology journals across 25 years revealed that, overall, women represented 40.2% of authors. This proportion is higher than in musicology [34.8% in @eerola2026inprep], in psychology more broadly [33.2% in @huang2020; 36.2% in @gonzalez2020women], and also much higher than in other STEM subjects of math, physics and computer science [15% in @huang2020] and topics such as astronomy and bioscience [17.8% in @son2022scientific]. Although our current findings suggests that the field of music psychology is doing better in fostering gender equity than some other fields, the distribution of authors by gender remains nonetheless unequal. In exploring the nuances behind this, we further analysed differences between authorship role, number of citations, geography, and article keywords.

In terms of authorship roles, notable authorship differences emerge. Women are more likely than men to appear as first authors, a trend that has become characteristic of the field only in the past 15 years. This is in line with previous research showing that female authorship representation is increasing [@gonzalez2020women; @ioannidis2023gender; @jemielniak2025gender; @sanchez2024analysis]. In contrast, we found that women remain underrepresented in the last authorship position, and this trend has not changed substantially over the last 15 years. This underrepresentation in woman as last authors is similar to the situation in medicine [@bruck2023bibliometric; @shah2021gender], psychology [@gonzalez2020women], and biology [@rock2021quantifying]. Although last authorship in the social sciences is not necessarily universally defined, it is nonetheless increasingly associated with seniority, supervisory responsibility, or principal investigator status [@drivas2024evolution]. Therefore, this underrepresentation suggests that women are less likely to occupy leadership roles such as lab heads or holders of substantial research resources. This pattern is consistent with broader evidence showing that women remain underrepresented in senior academic positions, including professorial appointments [@bakker2016tenure], invitations to contribute to journals, and authorship in high-prestige outlets [@holman2018gender]. Related analyses from science and medicine further show that women are more often associated with conducting experiments, whereas men are disproportionately represented in authorship roles linked to leadership and oversight [@macaluso2016science]. This pattern is also consistent with finding that women are more likely to drop away from academic careers with increasing seniority [@gonzalez2020women; @sanchez2024analysis]. Indeed, this gender gap could come from parenthood and parental leave, which account for about ~40% of gender gap in career advancement [@nielsen2024getting]. Fortunately, there are strides to improve the current situation, with opinion papers discussing way to improve receipt and reporting of intellectual credit [@banks2025women] as well as creating equitable environments in academic science [@martinez2024comparison]. In particular, one crucial aspect that has been highlighted to is the need for more mentorship programs for (junior) women to senior positions. Indeed, mentorship programs can encourage mentees to remain in academia [@gardiner2007show]. We note that within the broader music psychology community, there are already mentorship programs in place: for example, Women in Music Information Retrieval WIMIR (https://wimir.wordpress.com/) and the Society for Music Perception and Cognition (SMPC) has resources for trainees and a Mentorship committee (https://www.musicperception.org/committees) and often holds mentor-mentee meetings at conferences. Although these measures have been implemented for some years, it might still take some time for the effect to be reflected in authorship.

@@

In terms of eographical and cultural factors, our summaries of gender patterns across continents and countries indicate clear cross-national variation, supporting the idea that certain inequity may stem from national cultural factors [@bruck2023bibliometric]. Large Commonwealth nations, namely Australia, Canada, and the United Kingdom, seem to provide a academic climate more supportive of women in research, as reflected in the relatively high odds ratios of women appearing as authors (in any authorship position) in music psychology. This pattern, however, is not universal across all countries examined [@chan2020]. Prior work shows that women’s research success can be positively correlated with national indicators of gender equity [@chan2020] or are related to countries with intermediate Human Development Index [@sanchez2024analysis; @sugimoto2015relationship]. This discrepancy between author representation could likely to be related to a career length, which strongly correlates with overall productivity. Women exhibit higher dropout rates than men, particularly during the 5–10 years following their first publication [@huang2020], but policies geared towards equity and support for career breaks and caring responsibilities may well contribute towards the observed country-specific differences. Nevertheless, prior analyses demonstrate that even when women constitute a smaller share of researchers within a discipline or country, their contributions are often more impactful than those of their male colleagues [@chan2020]. When examining countries where women have significantly lower odds of authorship compared to men (Japan, Belgium, Austria, Sweden, and Turkey), it is not straightforward to conclude that the lower proportion of female author is related gender equality rankings. The notable exception is Turkey, which is positioned lower according to the Gender Inequality Index [@UNDPHDR2024].

The keyword analysis of the articles indicated thematic differences in the topics studied by women and men. Research areas related to children, well-being, health, and mental health were more frequently associated with women. This pattern is consistent with observations in psychology more broadly, where women are more strongly represented in sub-disciplines that focus on (health)care and nurturing [@bruck2023bibliometric; @gonzalez2020women]. The higher likelihood of women studying topics related to singing may be connected to prevailing gender stereotypes, or to the early negative perceptions of singing among boys [@Warzecha2013] and men [@palkki2015gender]. In contrast, topics related to cognition and computation were more often associated with men, which reflects a wider trend in psychology [@gonzalez2020women]. In a similar trend in computational linguistics, woman are more likely to publish on speech, social and conversational topics than males, who are more likely to publish in formal mathematical, syntax, and semantic approaches [@vogel2012he]. The difference that female prefer 'caring' topics over male authors fits with the general idea that female researchers value research on societal progress, while males prefer research aimed at scientific progress [@zhang2021gender]. This fits with another potential explanation for the disparity between authorship, namely that women faculty lean word and perform more university, campus, and departmental services than men in general [@guarino2017faculty]. Over time, performing such services to universities are time away from other work on acquiring funding and leading research, which would aggregate over time to time away from publishing research. It is nonetheless important for such services are completed; in some cases it could be there is more encouragement for males to take on these kinds of roles, but also it could be that success in academia could also be more societal defined as not only publications [@kiai2019protect], but as a whole should celebrate achievements that support internal, local and community services in a broader sense.

There are certain limitations of the current research. First, the gender of the authors are not part of the database - gender was inferred based on author name using _genderize API_ [@wais2006]. Nonetheless, we maintain that the current conclusions may still hold as both authors checked whether any of the gender attribution of major names needed fixing (see accompanying code). Additionally, gender attribution error was relatively small (only `89` had low (< 0.55) attribution probability, while 89.3% had high (> 0.90) attribution probability), so it is unlikely that the remaining names would significantly change the main conclusions. A second limitation is treating gender as a binary category. While we recognise that gender is a complex and multidimensional social construct, we used a binary male-female classification consistent with prior meta-science research on gender and authorship [@son2022scientific; @shah2021gender; @rock2021quantifying; @ni2021gendered; @gonzalez2020women; @wais2006] and because generally the number of non-binary authors is currently relatively low [0.8% in @son2022scientific]. Nonetheless, future research should also move towards using more inclusive, non-binary information. The third - and main - limitation is that such bibliometric research indicates the symptoms of academia issues, but not necessarily the causes. While we speculate on certain reasons for the current state of affairs as discussed, other kinds of research such as qualitative and longitudinal research would further elucidate the key problems, and where areas for improvements could be made to promote better equity in academia.

@@

The analysis of gender distributions in the five most prominent music psychology journals over the last 25 years presented a rich and evolving history of gender distribution in various authorship roles. While overall women hold smaller number of authorship overall (`{r} round(nrow(dplyr::filter(df,Gender=='female'))/nrow(df),3)*100`%), they are significantly more likely to hold first author positions in coauthored publications but significantly less likely likely to hold last author positions than men. For solo publications and being a coauthor, there were no significant gender differences.

@@

### Acknowledgements

We are grateful to Isabelle Peretz for suggesting a deeper look into the author types, and to our colleagues for their valuable input on the manuscript.

### 2025-09-27 manuscript/manuscript.qmd
Presubmission version, ready for colleagues to read.

# Discussion
A crucial marker of scholarly success in academia is authorship, which strongly influences career progression, recognition, funding, and advancement opportunities. However, there are several inequities within academic authorship, where women are often underrepresented. As male-female authorship representations differ across different academic disciplines, the goal of the current paper was to provide a snapshot of authorship prevalence and roles across gender in the field of music psychology. An analysis of papers from five core music psychology journals across 25 years revealed that, overall, women represented 40.2% of authors. This proportion is higher than in musicology [34.8% in @eerola2026inprep], in psychology more broadly [33.2% in @huang2020; 36.2% in @gonzalez2020women], and also much higher than in other STEM subjects of math, physics and computer science [15% in @huang2020] and topics such as astronomy and bioscience [17.8% in @son2022scientific]. Although our current findings suggests that the field of music psychology is doing better in fostering gender equity than some other fields, the distribution of authors by gender remains nonetheless unequal. In exploring the nuances behind this, we further analysed differences between authorship role, number of citations, geography, and article keywords.

@@

In terms of eographical and cultural factors, our summaries of gender patterns across continents and countries indicate clear cross-national variation, supporting the idea that certain inequity may stem from national cultural factors [@bruck2023bibliometric]. Large Commonwealth nations, namely Australia, Canada, and the United Kingdom, seem to provide a cultural climate more supportive of women in research, as reflected in the relatively high odds ratios of women appearing as authors (in any authorship position) in music psychology. This pattern, however, is not universal across all countries examined [@chan2020]. Prior work shows that women’s research success can be positively correlated with national indicators of gender equity [@chan2020] or are related to countries with intermediate Human Development Index [@sanchez2024analysis; @sugimoto2015relationship]. This discrepancy between author representation could likely to be related to a career length, which strongly correlates with overall productivity. Women exhibit higher dropout rates than men, particularly during the 5–10 years following their first publication [@huang2020], but policies geared towards equity and support for career breaks and caring responsibilities may well contribute towards the observed country-specific differences. Nevertheless, prior analyses demonstrate that even when women constitute a smaller share of researchers within a discipline or country, their contributions are often more impactful than those of their male colleagues [@chan2020]. When examining countries where women have significantly lower odds of authorship compared to men (Japan, Belgium, Austria, Sweden, and Turkey), it is not straightforward to conclude that the lower proportion of female author is related gender equality rankings. The notable exception is Turkey, which is positioned lower according to the Gender Inequality Index [@UNDPHDR2024].

@@

# Conclusions
The analysis of gender distributions in the five most prominent music psychology journals over the last 25 years presented a rich and evolving history of gender distribution in various authorship roles. While overall women hold smaller number of authorship overall (`{r} round(nrow(dplyr::filter(df,Gender=='female'))/nrow(df),3)*100`%), they are significantly more likely to hold first author positions in coauthored publications but significantly less likely likely to hold last author positions than men. For solo publications and being a coauthor, there were no significant gender differences.

>>>>

# Discussion

A crucial marker of scholarly success in academia is authorship, which strongly influences career progression, recognition, funding, and advancement opportunities. However, there are several inequities within academic authorship, where women are often underrepresented. As male-female authorship representations differ across different academic disciplines, the goal of the current paper was to provide a snapshot of authorship prevalence and roles across gender in the field of music psychology. An analysis of papers from five core music psychology journals across 25 years revealed that, overall, women represented 40.2% of authors. This proportion is higher than in musicology [34.8% in @eerola2026inprep], in psychology more broadly [33.2% in @huang2020; 36.2% in @gonzalez2020women], and also much higher than in other STEM subjects of math, physics and computer science [15% in @huang2020] and topics such as astronomy and bioscience [17.8% in @son2022scientific]. Although our current findings suggests that the field of music psychology is doing better in fostering gender equity than some other fields, the distribution of authors by gender remains nonetheless unequal. In exploring the nuances behind this, we further analysed differences between authorship role, number of citations, geography, and article keywords.

@@

In terms of eographical and cultural factors, our summaries of gender patterns across continents and countries indicate clear cross-national variation, supporting the idea that certain inequity may stem from national cultural factors [@bruck2023bibliometric]. Large Commonwealth nations, namely Australia, Canada, and the United Kingdom, seem to provide a academic climate more supportive of women in research, as reflected in the relatively high odds ratios of women appearing as authors (in any authorship position) in music psychology. This pattern, however, is not universal across all countries examined [@chan2020]. Prior work shows that women’s research success can be positively correlated with national indicators of gender equity [@chan2020] or are related to countries with intermediate Human Development Index [@sanchez2024analysis; @sugimoto2015relationship]. This discrepancy between author representation could likely to be related to a career length, which strongly correlates with overall productivity. Women exhibit higher dropout rates than men, particularly during the 5–10 years following their first publication [@huang2020], but policies geared towards equity and support for career breaks and caring responsibilities may well contribute towards the observed country-specific differences. Nevertheless, prior analyses demonstrate that even when women constitute a smaller share of researchers within a discipline or country, their contributions are often more impactful than those of their male colleagues [@chan2020]. When examining countries where women have significantly lower odds of authorship compared to men (Japan, Belgium, Austria, Sweden, and Turkey), it is not straightforward to conclude that the lower proportion of female author is related gender equality rankings. The notable exception is Turkey, which is positioned lower according to the Gender Inequality Index [@UNDPHDR2024].

@@

# Conclusions

The analysis of gender distributions in the five most prominent music psychology journals over the last 25 years presented a rich and evolving history of gender distribution in various authorship roles. While overall women hold smaller number of authorship overall (`{r} round(nrow(dplyr::filter(df,Gender=='female'))/nrow(df),3)*100`%), they are significantly more likely to hold first author positions in coauthored publications but significantly less likely likely to hold last author positions than men. For solo publications and being a coauthor, there were no significant gender differences.
